Models

### 2021-01-15 analysis/model_metrics.Rmd
Update plots

Get data and put it in long form 
```{r}
pins::board_register_github(repo = "karinorman/biodivTS", branch = "master")

@@

# model for overall trend (random effect w/varying intercept and slope)
metric_slope_fit <- metrics %>%
  filter(!is.na(value)) %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~lmer(logvalue ~ year + (1 + year | rarefyID), data = .x)))

metric_slope_coef <- metric_slope_fit %>%
  mutate(coef = map(model, tidy)) %>% 
  #mutate(confint = map(model, confint)) %>%
  select(-data, -model) %>% 
  unnest(cols = c(coef))

# metric_pred_fit <- metrics %>%
#   filter(!is.na(value)) %>%
#   group_nest(metric) %>%
#   mutate(model = map(data, ~lmer(logvalue ~ year + climate + taxa + (1|study_id/rarefyID), data = .x)))
# 
# metric_mean_coef_base <- metric_mean_fit_base %>%
#   mutate(coef = map(model, tidy)) %>% 
#   mutate(confint = map(model, confint)) %>%
#   select(-data, -model) %>% 
#   unnest(cols = c(coef))
# 
# metric_mean_coef <- metric_mean_fit %>%
#   mutate(coef = map(model, tidy)) %>% 
#   #mutate(confint = map(model, confint)) %>%
#   select(-data, -model) %>% 
#   unnest(cols = c(coef))
```

@@

>>>>

Get data and put it in long form 
```{r}
pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master")

@@

# model for overall trend (random effect w/varying intercept and slope)
# metric_slope_fit <- metrics %>%
#   filter(!is.na(value)) %>%
#   group_nest(metric) %>%
#   mutate(model = map(data, ~lmer(logvalue ~ year + (1 + year | rarefyID), data = .x)))
# 
# metric_slope_coef <- metric_slope_fit %>%
#   mutate(coef = map(model, tidy)) %>% 
#   #mutate(confint = map(model, confint)) %>%
#   select(-data, -model) %>% 
#   unnest(cols = c(coef))
```

@@

Plot of S and diversity metrics
```{r}
indiv_ts_coef %>%
  filter(term == "year", metric %in% c("FRic", "FEve", "FDiv", "FDis", "S")) %>%
  select(metric, estimate) %>% 
  ggplot() +
  geom_histogram(aes(x = estimate)) + #,
                 #binwidth = 2) +
  scale_x_continuous(name = 'slope') +
  #scale_y_continuous(breaks = c(0,2500,5000,7500,10000,12500, 15000, 17500, 20000,22500)) +
  labs(tag = 'B',
       y = 'Number of cells') +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank()) +
  facet_wrap(vars(metric), scales = "free")
```
